\documentclass{article}
\usepackage[top=20mm,left=20mm,right=15mm]{geometry}
\begin{document}



\section{Problem Validation}

Before starting the design, we conducted a problem validation exercise. This was done using a structured questionnaire distributed in the municipal council area.

\subsection{Questionnaire Design}

The questionnaire contained 13 questions covering the following areas:
\begin{itemize}
    \item The type of streetlights currently in use.
    \item How streetlights are currently switched on and off.
    \item How often lights remain on during the day.
    \item How often faults occur and what types of faults are common.
    \item How faults are currently detected and how long detection takes.
    \item The problems caused by delayed fault detection.
    \item Whether stakeholders believe an automated system would be useful.
    \item Their concerns about such a system.
\end{itemize}

\subsection{Key Findings}

The responses to the questionnaire confirmed the following:
\begin{itemize}
    \item A significant number of respondents reported that streetlights staying on during the daytime was either a frequent or occasional occurrence in their area.
    \item Streetlight faults were reported to occur often, with bulb failure is being the most common fault types.
    \item Most faults were detected through public complaints and routine inspections, rather than through any automated system.
    \item In many cases, identifying a faulty streetlight took more than one day.
    \item The main concerns raised by respondents were installation cost, reliability, and maintenance complexity.
\end{itemize}

\subsection{Conclusion from Validation}

The validation survey confirmed that the problems we identified are real and significant. It also confirmed that the proposed solution would be welcomed by the people who manage and depend on streetlights. The concerns raised about cost and reliability guided our design decisions, particularly our choice to use low-cost, widely available components and a simple but robust circuit design.
\end{document}